### 2012-06-18 inst/examples/value_of_information_allee.Rmd
new runs
table of final results

`ro cache=TRUE, warning=FALSE, comment=NA, message=FALSE, cache.path="value_of_information/", verbose=TRUE or`

@@

  list(sims = sims, opt = opt, true_stochasticity = c(true_g, true_m, true_i))
}
````

Corner cases

``` {r }
base <- simulatereps(det, 0, 0, 0)
reckless <- simulatereps(det, .1, .1, .1)
````

``` {r }
full <- simulatereps(gmi, .1, .1, .1)
cautious <- simulatereps(gmi, 0, 0, 0)
````

``` {r tidy}
sims <- list(base = base$sims, full = full$sims, reckless=reckless$sims, cautious=cautious$sims)
dat <- melt(sims, id=names(sims[[1]][[1]]))  
dt <- data.table(dat)
setnames(dt, c("L2", "L1"), c("reps", "uncertainty")) # names are nice
````

@@

``` {r  onerep}
ggplot(subset(dt,reps==1)) +
  geom_line(aes(time, fishstock)) +
  geom_line(aes(time, harvest), col="darkgreen") + 
  facet_wrap(~uncertainty) 
````

@@

``` {r  fig.cap="the induced dynamics in the stock size over time, for all replicates, by scenario"}
p1 <- ggplot(dt) 
p1 + geom_line(aes(time, fishstock, group = reps), alpha = 0.1) + facet_wrap(~uncertainty)
````

``` {r fig.cap="The profits made in each time interval of a single replicate, by scenario"}
ggplot(subset(dt,reps==1)) +
  geom_line(aes(time, profit))  + facet_wrap(~uncertainty)

@@

``` {r fig.cap="the distribution of profits by scenario"}
profits <-dt[ , sum(profit), by=c("reps", "uncertainty")] 
ggplot(profits) + geom_histogram(aes(V1)) + facet_wrap(~uncertainty)
````

@@

``` {r cache=FALSE}
profits[, mean(V1), by=uncertainty]
profits[, sd(V1), by=uncertainty]
````

>>>>

`ro cache=TRUE, warning=FALSE, comment=NA, message=FALSE, cache.path="value_of_information_allee/", verbose=TRUE or`

@@

#  list(sims = sims, opt = opt, true_stochasticity = c(true_g, true_m, true_i))
  sims
}
````

All cases

``` {r runallsims} 
policyfn <- list(det=det, g=g, m=m, i=i, gm=gm, gi=gi, gmi=gmi)
noise <- list(s0=c(0,0,0), sg=c(.2, 0, 0), sm=c(0, .2, 0), si=c(0,0,.2), sgm=c(.2, .2, 0), sgi=c(.2, 0, .2), sgmi=c(.2, .2, .2)) 
allcases <- lapply(policyfn, function(policyfn_i){
  lapply(noise, function(noise_i){
    simulatereps(policyfn_i, noise_i[1], noise_i[2], noise_i[3])
  })
})
````

``` {r tidyall}
sims <- unlist(allcases, recursive=FALSE)
dat <- melt(sims, id=names(sims[[1]][[1]]))  
dt <- data.table(dat)
setnames(dt, c("L2", "L1"), c("reps", "uncertainty")) # names are nice
````

@@

``` {r  onerep, dependson="tidyall"}
ggplot(subset(dt,reps==1)) +
  geom_line(aes(time, fishstock)) +
  geom_line(aes(time, harvest), col="darkgreen") + 
  facet_wrap(~uncertainty) 
````

@@

``` {r stock, fig.cap="the induced dynamics in the stock size over time, for all replicates, by scenario", dependson="tidyall"}
p1 <- ggplot(dt) 
p1 + geom_line(aes(time, fishstock, group = reps), alpha = 0.1) + facet_wrap(~uncertainty)
````

``` {r profits_time, fig.cap="The profits made in each time interval of a single replicate, by scenario", dependson="tidyall"}
ggplot(subset(dt,reps==1)) +
  geom_line(aes(time, profit))  + facet_wrap(~uncertainty)

@@

``` {r profits, fig.cap="the distribution of profits by scenario", dependson="tidyall"}
profits <-dt[ , sum(profit), by=c("reps", "uncertainty")] 
ggplot(profits) + geom_histogram(aes(V1)) + facet_wrap(~uncertainty)
````

@@

``` {r summarystats, cache=FALSE}
means <- profits[, mean(V1), by=uncertainty]
sds <- profits[, sd(V1), by=uncertainty]
````

``` {r prettytable, cache=FALSE, results="asis"}
require(xtable)
uncertainties <- c("deter", "growth", "measure", "implement", "growth+measure", "growth+implement", "all")
print(xtable(matrix(means$V1, nrow=7, dimnames=list(uncertainties, uncertainties))), type="html")
print(xtable(matrix(sds$V1, nrow=7, dimnames=list(uncertainties, uncertainties))), type="html")
````
